%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Junior Data Scientist} % Job title
    {Remedy Partners} % Organization
    {New York, New York} % Location
    {Aug 2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed XGBoost model to predict patient discharge location using current and historical medical information.\\
        Worked on series of classifiers to predict future medical procedures at a patient level.}
        \item {Used AWS Athena to query medical claims and construct tabular datasets from time-series data.}
        \item {Owned and developed a library of tools to facilitate rapid model prototyping and organized metric reporting. 
        Integrated \\with MLFlow to allow users to easily share results and ease knowledge transfer.}
        \item {Performed process mining using CSPADE and BupaR. Identified statistically significant sequences of medical codes to be\\ 
        used as features in future models. Findings also used to drive scoping sessions with product and clinical teams.\\ Packaged
        process to be easily used by other team members.}
        \item {Worked alongside engineering team to deploy models and debug pipelines.}
        \item {Helped develop internal best practices to ease deployment and code maintenance.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Science Intern} % Job title
    {Remedy Partners} % Organization
    {New York, New York} % Location
    {Jun. 2018 - Aug. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed improved regression model to predict skilled nursing facility length of stay using scikit-learn and XGBoost.}
        \item {Gained experience in using AWS EC2 to train models and perform computationally expensive operations.}
        \item {Conducted data exploration in Jupyter. Revealed key insights into inefficiencies regarding patient release.}
        \item {Created visualizations to present model performance and other statistics.}
        \item {Presented results and findings to company-wide audience including upper management.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
